Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-06 main.tex
Updated figure of experimental setup with camera and second tablet

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{experimental_setup}
    \caption{Our experimental setup: face-to-face interaction with a Nao robot.
    The robot writes on the tactile tablet, the child then corrects the robot by
    directly overwriting its letters on the tablet, with a stylus directly. An adult
    (either a therapist or an experimenter, depending on the studies), remains next
    to the child to guide the work (prompting, turn taking, etc.).}
    \label{experimental_setup}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{experimental_setup}
    \caption{Our experimental setup: face-to-face interaction with a Nao robot.
    The robot writes on the tactile tablet, the child then corrects the robot by
    directly overwriting its letters on the tablet, with a stylus directly. An adult
    (either a therapist or an experimenter, depending on the studies), remains next
    to the child to guide the work (prompting, turn taking, etc.). For some studies, a second tablet and an additional camera (dashed) are employed.}
    \label{experimental_setup}
\end{figure}
